### 2015-01-13 paper/Content/02research.tex
abstract proposal.
Common Android Development Approach continuation

\subsection{Concepts & Components of \emph{Android} Applications}

@@

Since the building components are managed by the system and dependent on each others implementation, one aspect that is inheritly difficult is testability. It is a challenge to divide business logic from the framework as it needs to react to certain system events -- as activity creation or destruction -- in order to be compatible to \emph{Android}. Another area

>>>>

\subsection{Concepts \& Components of Android Applications}

@@

Since the building components are managed by the system and dependent on the implementations, one aspect that is inherently difficult is \emph{testability}. It is a challenge to divide business logic from the framework as it needs to react to certain system events -- like activity destruction, which may be forced by the system at any point in time and need to be appropriately handled by the developer.

Other common difficulties developers face lie with the \emph{maintainability} and \emph{extensibility} of their software. Given the \emph{Android} framework, its many components and classes that enable communication between these compontents, the structure often gets cluttered -- especially in larger application projects. For example, \emph{ListView}s\footnote{Component to \enquote{display a list of scrollable items}. \cite{SDKListView}} need \emph{Adapter}\footnote{Class to \enquote{bridge between AdapterView and the underlying data}. \cite{SDKAdapter}} to display their content, which in turn might use \emph{Loader}s\footnote{Component that \enquote{performs asynchronous loading of data}. \cite{SDKLoader}} and \emph{Cursor}s\footnote{Interface class providing access to results of database queries. \cite{SDKCursor}} to fetch the data to display.

In addition \emph{portability} is a problem as business logic that is strongly intertwined when developing for the \emph{Android} platform cannot easily be ported to other platforms.

### 2015-01-13 paper/Content/sources.tex
Common Android Development Approach continuation

>>>>

\bibitem{SDKListView}
Google Inc., \emph{Android Developers -- List View},
[Online]. http://developer.android.com/guide/topics/ui/layout/listview.html (retrieved 11-Jan-2015)

\bibitem{SDKAdapter}
Google Inc., \emph{Android Developers -- Adapter},
[Online]. http://developer.android.com/reference/android/widget/Adapter.html (retrieved 11-Jan-2015)

\bibitem{SDKLoader}
Google Inc., \emph{Android Developers -- Loader},
[Online]. http://developer.android.com/reference/android/content/Loader.html (retrieved 11-Jan-2015)

\bibitem{SDKCursor}
Google Inc., \emph{Android Developers -- Cursor},
[Online]. http://developer.android.com/reference/android/database/Cursor.html (retrieved 11-Jan-2015)
